### 2017-01-04 robust-software.tex
Clarifying configuration files

\section{Allow configuration of all useful parameters from the command line.}

Useful parameters are those values that a user will need to modify to suit
their computer, dataset or application. 
The full list of useful parameters is software-specific and so cannot be
detailed here, but a short list includes providing
input and reference files and directories,
output files and directories,
filtering,
tuning,
random number generation seeds,
and
alternatives such as compressing results,
use a variant algorithm,
or verbose output.

Allowing parameters to be specific on the
command line increases the flexibility and usability of the program. You
may have determined early in development that 0.58 is an optimal cluster threshold for your
original dataset, but that doesn't mean it is best for every
case. Being able to change parameters on the fly to determine if and how
they change the results is important as your software gains more users,
as it facilitates exploratory analysis and parameter sweeping.

\textbf{Choose reasonable defaults where they exist},
and \textbf{set no defaults at all when there aren't any reasonable ones}.
You can set reasonable default values
as long as any command line arguments
override those values. Configuration files should be used in preference
to hard-coding the defaults directly. Configuration files can be in a standard
location, e.g. \texttt{.packagerc} in the user's home directory or
provided on the command line as an additional argument.
Only values that are unlikely to
change between runs belong in the config file, such as dependencies,
servers, version numbers, network drives, and any other defaults for
your lab or institution. 
Use a default configuration file and specify all other parameters on the
command line.

>>>>

\section{Make common operations easy to control.}

Being able to change parameters on the fly to determine if and how
they change the results is important as your software gains more users,
as it facilitates exploratory analysis and parameter sweeping.
Programs should therefore
\textbf{allow the most commonly changed parameters to be configured from the command line}.

Users will want to change some values more often than others.
Which ones is software-specific and so cannot be detailed here,
but a short list includes input and reference files and directories,
output files and directories,
filtering parameters,
random number generation seeds,
and
alternatives such as compressing results,
use a variant algorithm,
or verbose output.

To make programs even easier to use,
\textbf{choose reasonable defaults where they exist}
and \textbf{set no defaults at all when there aren't any reasonable ones}.
You can set reasonable default values
as long as any command line arguments
override those values.

Changeable values should \emph{never} be hard-coded:
if users have to edit your software in order to run it,
you have done something wrong.
Changeable but infrequently-changed values should therefore be stored in configuration files.
These can be in a standard location,
e.g. \texttt{.packagerc} in the user's home directory,
or provided on the command line as an additional argument.
Configuration files are often created during installation
to set up such things as server names,
network drives,
and other defaults for your lab or institution.
